%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
    \textbf{\Huge \scshape Raid Krenich} \\ \vspace{1pt}
    \small +1-226-724-6260$|$ \href{mailto:krenichraid@gmail.com}{\underline{krenichraid@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/krenich}{\underline{Linkedin}} $|$
    \href{https://github.com/Krenich09}{\underline{Github}} $|$
    \href{https://rq1d.itch.io/}{\underline{Itch.io}}
\end{center}

%
%\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%  \textbf{\href{http://sourabhbajaj.com/}{\Large Raid Krenich}} & Email : \href{mailto:krenichraid@gmail.com}{krenichraid@gmail.com}\\
%  \href{}{} & Mobile : +1-226-724-6260 \\
%\end{tabular*}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Windsor}{\textbf{Sep. 2023 - April 2027}}
      {Bachelor of Computer Science Honours}{}
        \resumeItemListStart{}
          \resumeItem{\textbf{Relevant coursework}: Algorithm Design, Software Engineering Principles, Operating Systems, Computer Networks, Web Development, Data Structures, Machine Learning.}
          \resumeItem{\textbf{Minor \& Specialization}: Business Administration, Game Development}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, Typescript, C\#, C, C++, Python, Java, HTML/CSS} \\
     \textbf{Developer Tools \& Frameworks}{: Node.js, Express, Electron.js, React, NextJS, Postgres, Docker, Unity, Git, Android Studio, OpenAI, Google Gemini, React, Microsoft Azure, Photon Networking PUN2, Stripe}
    }}
 \end{itemize}
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Basement Dweller Games }{Windsor, ON}
      {Lead Game Programmer}{Nov 2023 - Present}
      \resumeItemListStart
        \resumeItem{Led the development of captivating game projects using Unity3D, ensuring the implementation of cutting-edge features for an enhanced player experience.}
        \resumeItem{Designed and developed complex algorithms to ensure a smooth Player Controller, incorporating the latest trends in gaming for a seamless and immersive gameplay experience.}
      \resumeItemListEnd
      \resumeSubheading
      {Krenich Studios }{Remote}
      {Founder}{May 2022 - Present}
      \resumeItemListStart
        \resumeItem{\textbf{Innovative Mobile Game Development}}
        {Pioneered the development of three successful titles at Krenich Studios, introducing captivating experiences in the form of two mobile games, "Hyroute" and "Cube Stack," alongside the widely acclaimed online game "Backrooms with Friends," amassing thousands of downloads.}
        \resumeItem{\textbf{Full Stack Web Development:}}
        {Demonstrated ability to build websites and SaaS from start to finish, creating an AI Resume Generation Service "Quick Resume", and a code-comment AI generator "Codeloom".}
      \resumeItemListEnd
      
        \resumeSubheading
      {Fiverr}{Remote}
      {Freelance Game Developer and Coach}{Oct 2022 - May 2023}
      \resumeItemListStart
        \resumeItem{\textbf{Unity Game Development Instructor}}
        {Provided freelance services on Fiverr as a Game Developer and Coach, teaching both fundamental and advanced aspects of Unity Game Development.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

  


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  \resumeSubItem{ \href{https://quickresume.co/?ref=res}{\underline{\textbf{Quick Resume}}}{\textbf{ (2024)}}}
    \begin{flushleft}
      {Developed an AI-powered tool that generates multiple unique, professional, and ATS-readable resumes in minutes. Featured on Product Hunt, this tool has assisted numerous users in creating standout resumes.}
       \end{flushleft}
  \resumeSubItem{ \href{https://code-loom.com/?ref=res}{\underline{\textbf{Codeloom AI}}}{\textbf{ (2023)}}}
    \begin{flushleft}
      {Developed an AI code-comment generator that helps developers save time on creating documentation for any programming language.}
       \end{flushleft}
  \resumeSubItem{\textbf{PrayerTime (2024)}}
    \begin{flushleft}
    A cross-platform desktop app (Electron.js) for Muslims to manage daily prayers with customizable reminders and calculation methods.
    \end{flushleft}
    \resumeSubItem{\textbf{Backrooms With Friends (2023)}}
    \begin{flushleft}
    Online horror multiplayer game with procedural animation, level generation, and 2000+ downloads for a chilling and immersive experience.
    \end{flushleft}

    \resumeSubItem{\textbf{Hyroute (2021)}}
    \begin{flushleft}
      {Published an endless runner casual game on Google Play, offering a simple yet engaging gaming
experience to a wide audience.}
      \end{flushleft}
    \resumeSubItem{\textbf{Cube Stack (2023)}}
      {A visually stunning casual endless game on Google Play, developed in three days.}


%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%


%-------------------------------------------
\end{document}